Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-11-11 fib2.tex
show how gluing gives F-move

We list the axioms for a \emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
For the details of this construction, see
\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2004.}

For our purposes a \emph{surface} will be an
oriented $2$-dimensional manifold with boundary.
Each boundary component is labelled with
an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
This is the set of ``anyon labels'', and comes
equiped with an involution $\hat{}$ such that $\hat{1}=1.$
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
Each boundary component inherits the manifold orientation 
and contains a distinguished point.

We will mostly be concerned with \emph{planar} such
surfaces, ie. disc(s) with zero or more holes.
Note that we will not require surfaces themselves to be connected.

\newcommand{\F}{\mathscr{H}} % H or F ?
\newcommand{\C}{\mathbb{C}}

@@

{\bf Axiom I.}
The fusion space of an empty surface is one dimensional, 
$\F(\phi) \cong \C.$
For $M_a$ a disc with boundary label $a$ we have
$\F(M_1)\cong \C$ and 
$\F(M_a)\cong 0$ for $a\ne 1.$
For annulus $M_{a,b}$ with boundary labels
$a, b$ we have
$\F(M_{a,\hat{a}})\cong \C$ and 
$\F(M_{a,b})\cong 0$ for $a\ne \hat{b}.$

@@

{\bf Axiom III.}
%Gluing.
Denote a surface $M$ with (at least) two boundary
components labelled $a, b$ as $M_{a,b}$. 
Let $N$ be the surface obtained from $M$ by gluing
these two boundary components together.
If we constrain $b=\hat{a}$ then the fusion space
of $M_{a,\hat{a}}$ embedds unitarily in the fusion
space of $N.$ Moreover, there is a unitary map
$$
    \bigoplus_{a\in\mathbb{A}} \F(M_{a,\hat{a}}) \to \F(N).
$$
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.

>>>>

We list the axioms for a 
\emph{2-dimensional unitary topological modular functor}.
 % abbreviated as \emph{MF}.
There are quite alot of details that we leave out,
%For the details of this construction, see
see
\cite{Turaev1994}, \cite{Walker1991} or \cite{Bakalov2000}.
For a more pedestrian treatment, see \cite{Freedman2002simulation} or \cite{Beverland2014}.

\newcommand{\F}{\mathscr{H}} % H or F ?
\newcommand{\C}{\mathbb{C}}
\newcommand{\A}{\mathcal{A}}

For our purposes a \emph{surface} will be an
oriented $2$-dimensional manifold with boundary.
We will not require surfaces to be connected.
%Each boundary component is oriented (either explicitly or
%otherwise by using the orientation of the manifold)
Each boundary component will inherit the manifold orientation,
contain a distinguished point,
and be labelled with
%an element from a finite set $\mathbb{A}=\{1, a, b, c ...\}.$
an element from a finite set $\A.$
This is the set of ``anyon labels'', and comes
equiped with a vacuum element $\vac$ 
and an involution $\ \widehat{}\ $ such that $\widehat{\vac}=\vac.$

We will mostly be concerned with \emph{planar} such
surfaces, ie. disc(s) with zero or more holes.

@@

{\bf Axiom I.}
The fusion space of an empty surface is one dimensional, 
$\F(\phi) \cong \C.$
For $M_a$ a disc with boundary label $a$ we have
$\F(M_\vac)\cong \C$ and 
$\F(M_a)\cong 0$ for $a\ne \vac.$
For annulus $M_{a,b}$ with boundary labels
$a, b$ we have
$\F(M_{a,\widehat{a}})\cong \C$ and 
$\F(M_{a,b})\cong 0$ for $a\ne \widehat{b}.$

@@

{\bf Axiom III.}
%Gluing.
Denote a surface $M$ with (at least) two boundary
components labelled $a, b$ as $M_{a,b}$. 
Let $N$ be the surface obtained from $M$ by gluing
these two boundary components together.
Glueing must respect the orientation of the two boundary
components as well as identifying their distinguished points.
If we constrain $b=\widehat{a}$ then the fusion space
of $M_{a,\widehat{a}}$ embedds unitarily in the fusion
space of $N.$ Moreover, there is a unitary map
$$
    \bigoplus_{a\in\A} \F(M_{a,\widehat{a}}) \xrightarrow{\cong} \F(N).
$$
A common operation is to glue two separate surfaces.
We can do this by first taking disjoint union (tensoring
the fusion spaces)
and then gluing.

Here we show this process applied to two surfaces $M$ and $N$. 
\begin{center}
\includegraphics[]{pic-glue.pdf}
\end{center}
We display the surface $N$ with the $\widehat{a}$
boundary on the outside, 
to show more clearly how it fits into $M$.
In the glued manifold we
indicate the placement of $M$ and $N$ and the seam
along which glueing occured,
as well as the identification of distinguished points.

%\emph{XXX show marked point on boundaries ?}

\emph{XXX show orientation of boundaries ?}
\emph{XXX displaymath direct sum}
\emph{XXX $N...$ show ellipses?}

A most important linear map, called an $F-$move,
is constructed from two applications of the
gluing isomorphism as follows.

\begin{widetext}
\begin{center}
\includegraphics[]{pic-glue-fmove.pdf}
\end{center}
\end{widetext}

Here we have shown a manifold $M_{abc}$ with 
three labelled boundaries, as well as two separate
ways of gluing pairs-of-pants to get $M.$
